Analysis paper

### 2021-05-24 analysis/analysis.Rmd
add median lines to score distribution plot and rescale

```{r}

p_combined <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges() + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ target_type, ncol = 1) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))

p <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges() + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ location_target) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))
```

@@

tbl <- scores_tables %>%
  merge(coverage_tables, all.x = TRUE, by = c("modellocation_target", "target_phase", "classification"))

pl <- (p_combined + p) / p_phases + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

@@

>>>>

```{r}
scores[, target_type := paste0(str_to_title(target_type), "s overall")]
p_combined <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ target_type, ncol = 1) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))

p <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ location_target) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50)) + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank())
```

@@

pl <- wrap_plots(p_combined, p, widths = c(1, 2)) / p_phases + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

@@

tbl <- scores_tables %>%
  merge(coverage_tables, all.x = TRUE, by = c("model", "target_phase", "classification"))
